Summary of tumor cell classification with `AUCell` for `r params$library_id`

### 2024-07-12 analyses/cell-type-ewings/template_notebooks/auc-workflow/01-auc-results.Rmd
update comments and text

```{r}
# add marker gene classification classifying cells based on expression of at least 1 marker gene  
marker_gene_class_df <- markers_df |> 
  dplyr::select(barcodes, sum_raw_exp) |> 
  dplyr::distinct() |> 
  dplyr::mutate(
    marker_gene_classification = dplyr::if_else(
      sum_raw_exp > 0,
      "Tumor",
      "Normal"

@@

classification_df <- classification_df |> 
  dplyr::left_join(marker_gene_class_df, by = "barcodes") |> 
  tidyr::pivot_longer(ends_with("classification"),
                      names_to = "method",
                      values_to = "classification") |> 
  dplyr::mutate(
    # make a factor so tumor always appears first 
    classification = forcats::fct_relevel(classification, "Tumor")
  )
```

@@

Below is a UMAP showing cells that are labeled as either `Tumor` or `Normal` using `AUCell`.

@@

The below plots summarize marker gene expression in tumor and normal cells as classified by `AUCell`.

@@

Here every row is a marker gene and every column is a cell with colors corresponding to the expression of a specified marker gene.  
The annotation bar indicates which cells are tumor or normal cells as classified by `AUCell`. 
We expect to see higher expression of individual marker genes in tumor cells compared to normal cells.

@@

The below plots summarize the gene set scores in tumor and normal cells as classified by `AUCell`.

@@

Here every column is a cell and every row is a gene set with colors corresponding to the gene set score. 
The annotation bar indicates which cells are tumor or normal cells as classified by `AUCell`. 
We expect to see higher gene set scores in tumor cells compared to normal cells.

>>>>

```{r}
# add marker gene classification based on expression of at least 1 marker gene  
marker_gene_class_df <- markers_df |> 
  dplyr::select(barcodes, sum_raw_exp) |> 
  dplyr::distinct() |> 
  dplyr::mutate(
    marker_gene_classification = dplyr::if_else(
      sum_raw_exp > 0,
      "Tumor",
      "Normal"

@@

# add classification to main classification data frame
classification_df <- classification_df |> 
  dplyr::left_join(marker_gene_class_df, by = "barcodes") |> 
  tidyr::pivot_longer(ends_with("classification"),
                      names_to = "method",
                      values_to = "classification") |> 
  dplyr::mutate(
    # make a factor so tumor always appears first 
    classification = forcats::fct_relevel(classification, "Tumor")
  )
```

@@

Below is a UMAP showing cells that are labeled as either `Tumor` or `Normal` using `AUCell` and marker gene expression.

@@

The below plots summarize marker gene expression in tumor and normal cells as classified by `AUCell` and marker gene expression. 
Note that we expect to see clear separation of gene expression for the marker gene classification as classification is based purely on expression.

@@

Here every row is a marker gene and every column is a cell with colors corresponding to the expression of a specified marker gene.  
The annotation bar indicates which cells are tumor or normal cells as classified by `AUCell` or marker gene expression. 
We expect to see higher expression of individual marker genes in tumor cells compared to normal cells.

@@

The below plots summarize the gene set scores in tumor and normal cells as classified by `AUCell` and marker gene expression.

@@

Here every column is a cell and every row is a gene set with colors corresponding to the gene set score. 
The annotation bar indicates which cells are tumor or normal cells as classified by `AUCell` and marker gene expression. 
We expect to see higher gene set scores in tumor cells compared to normal cells.
